Job Demands-Resources model components through the lens of O*NET classifications

### 2022-12-02 Submission.Rmd
Updating content of introduction

author: 
  - name          : "Alicia Stachowski"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Menomenie, WI"
    email         : "stachowskia@uwstout.edu"
  - name          : "Renata Garcia Prieto Palacios Roji"
    affiliation   : "2"
  - name          : "John Kulas"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "University of Wisconsin - Stout"
  - id            : "2"
    institution   : "Montclair State University"

@@

Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlight the importance of work characteristics on the experience of motivation and strain, which clearly have an impact on job performance. In light of some of the recent debate surrounding the challenge-hindrance stressor framework [e.g., @mazzola2019should], we extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, and how they relate to two important organizational outcomes: engagement and stress. Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.

@@

As implied in the last paragraph, job context and characteristics are “assigned” or appraised as demands or resources. Although some research on job demands in particular is based on apriori classifications of demands [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand. The stress process speaks to how such individual difference in appraisal is possible. @lazarus1984stress presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis. Via this process, meaning is assigned to stimuli – if appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping. The cycle of appraisal then continues based on the action to cope with the stressor [@lazarus1984stress].

@@

Although there is a tendency to attach a negative connotation to the word “stress”, @selye1936syndrome defined stress as a response to change, which is quite non-specific. We return to the employed public figure for this next section. It is quite probable that two employees would be called upon to serve as a spokesperson for their organization in a time of need. One may appraise the circumstance as an opportunity to positively influence others, while the other may plausibly feel paralyzed by the task. In fact, @bakker2017job call attention to different types of demands in their recent review of, and future directions, for work on the job-demands resources theory. The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor (@cavanaugh2000empirical). @cavanaugh2000empirical delineated between two forms of demands – that of *challenge* and *hindrance* demands. Challenge demands promote mastery, personal growth, and future gains – these stressors should lead to coping strategies that facilitate achievement. Stressors like time pressure and responsibility are considered challenge stressors/demands. hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors (e.g., role conflict, role ambiguity, politics) are associated with negative job behaviors and attitudes. This particular distinction between challenges and hindrances has been of value in determining what demands are related to various outcomes, whereby challenge stressors are typically associated with positive outcomes, and hindrance stressors, negative outcomes (e.g., @cavanaugh2000empirical).

However, one of the key questions we need to ask as researchers pertains to the very basic consideration of appraisals. In fact, this is one of several issues raised by @ mazzola2019should in a recent review and meta-analysis of this framework. These authors cited the apriori assignment to stressors as a challenge or hindrance as a flawed assumption, suggesting that stressors are more likely to be a combination of both – challenge and hindrance appraisals. @lepine2022challenge, in a rebuttal to the @ mazzola2019should criticism, while acknowledging that the original challenge-hindrance stressor framework was based on the assertion that people tend to appraise specific work stressors ad challenges and other demands, noted that the appraisals likely served as a mediator.

@@

We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point. @podsakoff2007differential supported the original assertion of @cavanaugh2000empirical with regard to work outcomes such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover. The opposite pattern of relationship was observed for hindrance stressors. @ kim2020thriving, similarly, found evidence for the differential results via challenge and hindrance appraisals

>>>>

author: 
  - name          : "Alicia Stachowski"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Menomenie, WI"
    email         : "stachowskia@uwstout.edu"
  - name          : "John Kulas"
    affiliation   : "2"
  - name          : "Renata Garcia Prieto Palacios Roji"
    affiliation   : "3"

affiliation:
  - id            : "1"
    institution   : "University of Wisconsin - Stout"
  - id            : "2"
    institution   : "eRg"
   - id            : "3"
    institution   : "PepsiCo"

@@

Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlight the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance. However, much of our existing knowledge of the way this model functions is grounded in the assumption that characteristics are generally considered resources or generally considered demands. We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (@webster2011extending) or that appraisals may change over time (CITE HERE). We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, which a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics. Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.

@@

As implied in the last paragraph, job context and characteristics are assigned or appraised as demands or resources. Although much of our research on job demands in particular is based on apriori classifications of demands [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand. The stress process speaks to how such individual difference in appraisal is possible. @lazarus1984stress presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis. Via this process, meaning is assigned to stimuli based on potential for gain or loss. If appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping. The cycle of appraisal then continues based on the action to cope with the stressor [@lazarus1984stress].

@@

Although there is a tendency to attach a negative connotation to the word “stress”, @selye1936syndrome defined stress as a response to change, which is quite non-specific. We return to the employed public figure for this next section. It is quite probable that two employees would be called upon to serve as a spokesperson for their organization in a time of need. One may appraise the circumstance as an opportunity to positively influence others, while the other may plausibly feel paralyzed by the task. In fact, @bakker2017job call attention to different types of demands in their recent review of, and future directions, for work on the job-demands resources theory.

The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor (@cavanaugh2000empirical). @cavanaugh2000empirical delineated between two forms of demands – that of *challenge* and *hindrance* demands. Challenge demands promote mastery, personal growth, and future gains – these stressors should lead to coping strategies that facilitate achievement. Stressors like time pressure and responsibility are considered challenge stressors/demands. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors (e.g., role conflict, role ambiguity, politics) are associated with negative job behaviors and attitudes. This particular distinction between challenges and hindrances has been of value in determining what demands are related to various outcomes, whereby challenge stressors are typically associated with positive outcomes, and hindrance stressors, negative outcomes (e.g., @cavanaugh2000empirical).

However, one of the key questions we need to ask as researchers pertains to the very basic consideration of appraisals. In fact, this is one of several issues raised by @mazzola2019should in a recent review and meta-analysis of this framework. These authors cited the apriori assignment to stressors as a challenge or hindrance as a flawed assumption, suggesting that stressors are more likely to be a combination of both – challenge and hindrance appraisals. @lepine2022challenge, in a rebuttal to the @ mazzola2019should criticism, while acknowledging that the original challenge-hindrance stressor framework was based on the assertion that people tend to appraise specific work stressors ad challenges and other demands, noted that the appraisals likely served as a mediator.

@@

We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point. @podsakoff2007differential supported the original assertion of @cavanaugh2000empirical with regard to work outcomes such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover. The opposite pattern of relationship was observed for hindrance stressors. @kim2020thriving, similarly, found evidence for the differential results via challenge and hindrance appraisals.
